Estimating Life-Stage Specific Habitat Capacity for Anadromous Salmonids using Quantile Random Forest Models

### 2019-12-24 analysis/R_scripts/fit_qrf_model.Rmd
re-compiled files on new Merck laptop. Incorporated snapPointsToLines_v2 function from QRFcapacity package.

# set snap distance (in meters)
st_crs(chnk_samps)
snap_dist = 1000

# which of those sites are in Chinook domain?
chnk_sites = chnk_samps %>%
  as_Spatial() %>%
  maptools::snapPointsToLines(chnk_domain %>%
                                mutate(id = 1:n()) %>%
                                select(id, MPG) %>%
                                as_Spatial(),
                              maxDist = snap_dist,
                              withAttrs = T,
                              idField = 'id') %>%
  as('sf') %>%
  select(-nearest_line_id, -snap_dist) %>%
  # include some sites in the John Day where Chinook were found (or seemed to be close to sites where Chinook were found)
  rbind(st_read('../data/derived_data/Chnk_JohnDay_TrueObs.shp',
                quiet = T) %>%
          st_transform(st_crs(chnk_domain)) %>%
          select(-in_range))

@@

# save some results
use_data(fish_hab, 
         hab_dict,
         hab_data,
         hab_avg,
         sel_hab_mets,
         qrf_data,
         dens_offset,
         qrf_mod,
         version = 2,
         overwrite = T)

@@

pred_hab_sites_chnk = pred_hab_sites %>%
  filter(!is.na(LON_DD)) %>%
  st_as_sf(coords = c('LON_DD', 'LAT_DD'),
           crs = 4326) %>%
  st_transform(crs = st_crs(chnk_domain)) %>%
  as_Spatial() %>%
  maptools::snapPointsToLines(chnk_domain %>%
                                mutate(id = 1:n()) %>%
                                select(id, MPG) %>%
                                as_Spatial(),
                              maxDist = snap_dist,
                              withAttrs = T,
                              idField = 'id') %>%
  as('sf') %>%
  as_tibble() %>%
  select(-nearest_line_id, -snap_dist, -geometry) %>%
  # add sites in the John Day
  bind_rows(st_read('../data/derived_data/Chnk_JohnDay_TrueObs.shp',
                    quiet = T) %>%
              as_tibble() %>%
              select(Site) %>%
              inner_join(pred_hab_sites))

>>>>

# set snap distance (in meters)
st_crs(chnk_samps)
max_snap_dist = 1000

# which of those sites are in Chinook domain?
chnk_sites = chnk_samps %>%
  as_Spatial() %>%
  snapPointsToLines_v2(points = .,
  # maptools::snapPointsToLines(points = .,
                              lines = chnk_domain %>%
                                mutate(id = 1:n()) %>%
                                select(id, MPG) %>%
                                as_Spatial(),
                              maxDist = max_snap_dist,
                              withAttrs = TRUE,
                              idField = 'id') %>%
  as('sf') %>%
  select(-nearest_line_id, -snap_dist) %>%
  # include some sites in the John Day where Chinook were found (or seemed to be close to sites where Chinook were found)
  rbind(st_read('../data/derived_data/Chnk_JohnDay_TrueObs.shp',
                quiet = T) %>%
          st_transform(st_crs(chnk_domain)) %>%
          select(-in_range))

@@

# save some results
usethis::use_data(fish_hab, 
                  hab_dict,
                  hab_data,
                  hab_avg,
                  sel_hab_mets,
                  qrf_data,
                  dens_offset,
                  qrf_mod,
                  version = 2,
                  overwrite = T)

@@

pred_hab_sites_chnk = pred_hab_sites %>%
  filter(!is.na(LON_DD)) %>%
  st_as_sf(coords = c('LON_DD', 'LAT_DD'),
           crs = 4326) %>%
  st_transform(crs = st_crs(chnk_domain)) %>%
  as_Spatial() %>%
  snapPointsToLines_v2(chnk_domain %>%
  # maptools::snapPointsToLines(chnk_domain %>%
                                mutate(id = 1:n()) %>%
                                select(id, MPG) %>%
                                as_Spatial(),
                              maxDist = snap_dist,
                              withAttrs = T,
                              idField = 'id') %>%
  as('sf') %>%
  as_tibble() %>%
  select(-nearest_line_id, -snap_dist, -geometry) %>%
  # add sites in the John Day
  bind_rows(st_read('../data/derived_data/Chnk_JohnDay_TrueObs.shp',
                    quiet = T) %>%
              as_tibble() %>%
              select(Site) %>%
              inner_join(pred_hab_sites))

### 2019-12-24 analysis/paper/paper.Rmd
re-compiled files on new Merck laptop. Incorporated snapPointsToLines_v2 function from QRFcapacity package.

```{r packages}
library(tidyverse)
library(QRFcapacity) # for the moment, until we know exactly what data to copy over to this repo
library(QRFpaper)
library(janitor)
library(knitr)

@@

```{r read-data}
# fish/habitat data for fitting QRF models
# data("fh_sum_champ_2017")
# fh_data = fh_sum_champ_2017 %>%
#   filter(Species == 'Chinook') %>%
#   mutate_at(vars(Watershed, Species, FishCrew),
#             list(fct_drop))

data("fh_sum_champ_2014")
fh_data = fh_sum_champ_2014 %>%
  filter(Species == 'Chinook') %>%
  mutate_at(vars(Watershed, Species, FishCrew),
            list(fct_drop))

@@

```{r load-qrf-model}
load('../data/derived_data/qrf_juv_summer.rda')
qrf_mod = qrf_mods[[1]]
qrf_data = qrf_mod_df %>%
  filter(Species == 'Chinook')
```

@@

```{r fh-samp-table}
# fh_data %>%
qrf_data %>%
  # filter(Year <= 2014) %>%
  tabyl(Watershed) %>%
  adorn_totals() %>%
  adorn_pct_formatting() %>%
  # select(-percent) %>%
  kable(caption = 'The number of unique sites in the initial dataset, by watershed, with paired fish-habitat data used to populate the spring/summer Chinook salmon parr capacity model')
```

@@

>>>>

```{r packages}
library(tidyverse)
# library(QRFcapacity) # for the moment, until we know exactly what data to copy over to this repo
library(QRFpaper)
library(janitor)
library(knitr)

@@

```{r read-data, eval = F}
# fish/habitat data for fitting QRF models
data("fh_sum_champ_2017")
fh_data = fh_sum_champ_2017 %>%
  filter(Species == 'Chinook') %>%
  mutate_at(vars(Watershed, Species, FishCrew),
            list(fct_drop))

# data("fh_sum_champ_2014")
# fh_data = fh_sum_champ_2014 %>%
#   filter(Species == 'Chinook') %>%
#   mutate_at(vars(Watershed, Species, FishCrew),
#             list(fct_drop))

@@

```{r load-qrf-model, eval = F}
load('../data/derived_data/qrf_juv_summer.rda')
qrf_mod = qrf_mods[[1]]
qrf_data = qrf_mod_df %>%
  filter(Species == 'Chinook')
```

@@

```{r fh-samp-table}
qrf_data %>%
  # filter(Year <= 2014) %>%
  tabyl(Watershed) %>%
  adorn_totals() %>%
  adorn_pct_formatting() %>%
  # select(-percent) %>%
  kable(caption = 'The number of unique sites in the initial dataset, by watershed, with paired fish-habitat data used to populate the spring/summer Chinook salmon parr capacity model')
```

@@

```{r sr-table}
